---
title: "APIs"
author: "Jan-Philipp Kolb"
date: "21 April 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## [Rspotify: Access to Spotify API via R](https://www.r-bloggers.com/my-new-r-package/)

```{r}
library(devtools)
install_github("tiagomendesdantas/Rspotify")
```

- [Token](https://developer.spotify.com/web-api/)

## [Uber API](https://www.r-bloggers.com/uber-a-package-for-the-uber-api/)


## Links

- [RSelenium: A wonderful tool for web scraping.](https://www.r-bloggers.com/rselenium-a-wonderful-tool-for-web-scraping/)

- [Statistics New Zealand experimental API initiative](https://www.r-bloggers.com/statistics-new-zealand-experimental-api-initiative/)

- [Webscraping with rvest: So Easy Even An MBA Can Do It!](https://www.r-bloggers.com/webscraping-with-rvest-so-easy-even-an-mba-can-do-it/)

- [Mapping and Web-scraping the 2016 Presidential Election Results in Connecticut](https://www.r-bloggers.com/mapping-web-scraping-the-2016-presidential-election-results-in-connecticut/)

- [Using Microsoft’s Emotion API to Settle an Old Argument](https://www.r-bloggers.com/using-microsofts-emotion-api-to-settle-an-old-argument/)


- [Scraping Web sources: Two illustrations](https://www.r-bloggers.com/scraping-web-sources-two-illustrations/)
