---
title: "R and D3"
author: "Jan-Philipp Kolb"
date: "7 Februar 2017"
output:
  slidy_presentation: default
  ioslides_presentation:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=F,warning=F,eval=T)
```

## [D3 Graph Gallery](http://christopheviau.com/d3list/gallery.html)

- [Combining the power of R and D3.js](https://www.ae.be/blog-en/combining-the-power-of-r-and-d3-js/)

- [Five Interactive R Visualizations With D3, ggplot2, & RStudio](http://moderndata.plot.ly/interactive-r-visualizations-with-d3-ggplot2-rstudio/)

## Interaktive Graphiken

- [R Interactive Graphics with SVG](http://timelyportfolio.github.io/gridSVG_intro/)

## [tabplotd3](https://cran.r-project.org/web/packages/tabplotd3/index.html)

- [Beispiel tabplot3d](http://www.datasciencecentral.com/profiles/blogs/r-for-big-data-in-one-picture)

```{r,eval=F}
install.packages("tabplotd3")
```


```{r tableplot}
library(tabplotd3)
require(ggplot2)
data(diamonds)
tableplot(diamonds)
```

## [gigvis](https://github.com/rstudio/ggvis)

```{r,eval=F}
install.packages("ggvis")
```


```{r}
library("ggvis")
library(dplyr)
```

- [Übersicht zu ggvis](http://ggvis.rstudio.com/)

## [Kochbuch für ggvis](http://ggvis.rstudio.com/cookbook.html)

```{r}
mtcars %>% ggvis(~wt, ~mpg) %>% layer_points()
```

## Plots mit Gruppierung

```{r}
mtcars %>% 
  ggvis(~wt, ~mpg, fill = ~factor(cyl)) %>% 
  layer_points() %>% 
  group_by(cyl) %>% 
  layer_model_predictions(model = "lm")
```

## [googleVis](https://cran.r-project.org/web/packages/googleVis/index.html)

```{r,eval=F}
install.packages("googleVis")
```


```{r}
library(googleVis)
```

```{r}
df <- data.frame(year=1:11, x=1:11,
                 x.scope=c(rep(TRUE, 8), rep(FALSE, 3)),
                 y=11:1, y.html.tooltip=LETTERS[11:1],                 
                 y.certainty=c(rep(TRUE, 5), rep(FALSE, 6)),
                 y.emphasis=c(rep(FALSE, 4), rep(TRUE, 7)))
plot(
  gvisScatterChart(df,options=list(lineWidth=2))
)
```

```{css}
body {
  color: red;
  background: #000000;
}
```

## 

[SVGAnnotation](https://www.jstatsoft.org/article/view/v046i01)


```{r,eval=F}
install.packages("SVGAnnotation")
```


## [Click me](http://rclickme.com/)

```{r,eval=F}
install.packages("devtools")
library(devtools)

install_github("clickme", "nachocab")
```

```{r,eval=F}
library(clickme)

# simple
clickme("points", 1:10)

# fancy
n <- 500
clickme("points",
    x = rbeta(n, 1, 10), y = rbeta(n, 1, 10),
    names = sample(letters, n, r = T),
    color_groups = sample(LETTERS[1:3], n, r = T),
    title = "Zoom Search Hover Click")
```

## [d3Network ](http://christophergandrud.github.io/d3Network/)

```{r,eval=F}
install.packages("d3Network")
```

```{r}
library(d3Network)
Source <- c("A", "A", "A", "A", "B", "B", "C", "C", "D")
Target <- c("B", "C", "D", "J", "E", "F", "G", "H", "I")
NetworkData <- data.frame(Source, Target)
d3SimpleNetwork(NetworkData, width = 400, height = 250)
```


```{r,eval=F}
sink("FirstNetwork.js") 

writeLines(d3SimpleNetwork(NetworkData), fileConn)
unlink("FirstNetwork.js")
```



## [Rook](https://cran.r-project.org/web/packages/Rook/index.html)

```{r,eval=F}
install.packages("Rook")
```


## Links

- [Google Charts](https://developers.google.com/chart/interactive/docs/gallery/geochart)

- [Three little circles](https://bost.ocks.org/mike/circles/)

- [Wie schreibt man gute html widgets](http://deanattali.com/blog/htmlwidgets-tips/)

- [R wie Javascript programmieren](https://blog.semicolonsoftware.de/programming-r-like-its-javascript-python/)